---
title: Regression Homework
author: Andrew Vandenberg
date: April 24, 2021
output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: github
    math: katex
    number_sections: true
---

# Import the `mlbattendance2015` data set from project 2 into R.

```{r message =FALSE}
library(tidyverse)
library(readxl)
mlb <- read_excel("mlbattendance2015.xlsx")
```

# Build a regression model to predict average attendance from Winning Percentage (`Winpct`).  Also provide a graphical summary of the relationship.

```{r}
avg_att <- lm(avgattendance ~ winpct, mlb)
avg_att

ggplot(avg_att, aes(x = winpct, y = avgattendance)) +
  geom_point(color = "red") + 
  geom_smooth(method = "lm") +
  labs(x = "Win %", y = "Avg Attendance", title = "Win % versus Avg Attendance") +
  theme_bw()
  
summary(avg_att)
```

# Next, add League as a predictor to the previous model, in a parallel lines model.

```{r}
mlb$League = factor(mlb$League) 

avg_att2 <- lm(avgattendance ~ winpct + League, mlb)
avg_att2

ggplot(avg_att2, aes(x = winpct, y = avgattendance, color = League)) +
  geom_point(color = "red") + 
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()

summary(avg_att2)
```

# Finally, add potential interaction between League and Winning Percentage as a predictor, creating a possible non-parallel lines model.


```{r}
avg_att3 <- lm(avgattendance ~ winpct + League + winpct:League, mlb)
avg_att3

summary(avg_att3)
```


# Provide a graph of the data that incorporates both winning percentage and league as predictors and avg attendance as the response.

```{r}
ggplot(avg_att2, aes(x = winpct, y = avgattendance, color = League)) +
  geom_point(color = "red") + 
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
  
```

# Which of the models in (2), (3), and (4) do you think is the best?  Clearly justify your answer.

The model from question 3 (`avg_att2`) is the best model because it has the highest adjusted $R^2$ value (0.25 vs 0.19 (`avg_att`) and 0.23 (`avg_att3`)).

|Model  | Adjusted $R^2$ | 
|--------|--------------------|
|`avg_att` | 0.19 | 
| `avg_att2` | 0.25   | 
| `avg_att3` | 0.23  | 


# Predict average attendance for an American League team with a 60% winning percentage, and for a National League Team with a 50% winning percentage based upon your best model from steps (2), (3), (4).

```{r}

newdata <- tibble(League = c("National"), winpct = c(50))
newdata2 <- tibble(League = c("American"), winpct = c(60))

National_mod1 <- predict(avg_att, newdata, se.fit = FALSE)
National_mod2 <- predict(avg_att2, newdata, se.fit = FALSE)
National_mod3 <- predict(avg_att3, newdata, se.fit = FALSE)


American_mod1 <- predict(avg_att, newdata2, se.fit = FALSE)
American_mod2 <- predict(avg_att2, newdata2, se.fit = FALSE)
American_mod3 <- predict(avg_att3, newdata2, se.fit = FALSE)

```

-----------------------------------------------------------------------------
|Model  | Prediction Value | 
|--------|--------------------|
|`National_mod1` | 28900.82  | 
| `National_mod2` | 31376.33   | 
| `National_mod3` | 31332.66   | 
|`American_mod1` | 35091.91  | 
| `American_mod2` | 33032.54    | 
| `American_mod3` | 34956.55   | 


